Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-30 W13report.tex
Added captions and MSE figs

Using this simplified data set, we can begin to look at how we may predict 
optimal configs based measured statistics.  We notice that the MSE of the
control sample has a minimum in all cases.  See Figures \ref{fig-MSE_CONTROL}
and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
fitted sample respectively.  We note that the config at the minimum MSE value is
not always the same config.  Table \ref{tab-bestconfig_MSE} lists the configs
at the minimum of the MSE for the control sample.  This can be compared to
the configs in Table \ref{tab-bestconfig10}.

@@

\begin{figure}%
\captionsetup[subfloat]{labelformat=empty}
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
\caption{}
\label{fig-fp_v_thresh}
\end{figure}

>>>>

Using this simplified data set, we can begin to look at how we may predict 
optimal configs based measured statistics.  We notice that the MSE of the
control sample has a minimum in all cases.  See Figures \ref{fig-MSE_CONTROL}
and \ref{fig-MSE_FITTED} to see the behavior of the MSE for the control sample and
fitted sample respectively.  In the control case there is a minimum indicating that 
the the model is overfit while the fitted sample continues to decrease despite the 
increasing complexity.  For more discussion on this you can see Section $8.11$ in
\cite{TheSecondBestBook}.

We note that the config at the minimum MSE value is
not always the same config.  Table \ref{tab-bestconfig_MSE} lists the configs
at the minimum of the MSE for the control sample.  This can be compared to
the configs in Table \ref{tab-bestconfig10}.

@@

\begin{figure}%
\captionsetup[subfloat]{labelformat=empty}
\centering
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_nocorr.eps}}
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_nocorr.eps}}\\
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_01_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_02_corr.eps}}%
\subfloat[]{\includegraphics[width=0.3\textwidth]{figures/fp_v_thresh_03_corr.eps}}%
\caption{Here we show the comparison of detected false positive count to the analytic predition.
In all cases the blue circles are the prefilter case and the red squares are the postfilter case.  
The top row has had the counts corrected for the underestimate of the noise by the variance plane.  This is a 
1\% correction in the case of prefiltering and a 4\% correction to the variance in the postfiltering case.
In the bottom row we have corrected the predicted counts to coincide with the measured values.  From left to right
this is a 5\%, 3\%, 2\% correction to the variance respectively.  The shaded area is the 1-$\sigma$ confidence envelope
determined from Monte Carlo simulations assuming the analytic form of the false positive rate and a Gaussian distribution.}
\label{fig-fp_v_thresh}
\end{figure}

\begin{figure}%
\centering
\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_PREFILTER.eps}}
\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_CONTROL_POSTFILTER.eps}}
\caption{We plot the $\langle MSE \rangle$ for each visit using the control sample which was not used in the
model fitting.  The left is for the prefiltering case and the right is for the 
postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because the minimum MSE came
from these for all visits.  The top pane in the postfiltering case just shows the spatial order since the other 
values are held constant in the case that deconvolution is requested.  Notice that all visits have a minimum.
Compare this to the same statistic calculated on the fitted sample in Figure \ref{fig-MSE_FITTED} where there is no minimum.}
\label{fig-MSE_CONTROL}
\end{figure}

\begin{figure}%
\centering
\subfloat[PREFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_PREFILTER.eps}}
\subfloat[POSTFILTERED]{\includegraphics[width=0.49\textwidth]{figures/MSE_FITTED_POSTFILTER.eps}}
\caption{We plot the $\langle MSE \rangle$ for each visit using the sample used in the model fitting.  
The left is for the prefiltering case and the right is for the 
postfiltering case.  In each case we have plotted only the nGauss=3 and spatial order=(4,5,6) because we find that a spatial
order of at least 4 is needed.  The top pane in the postfiltering case just shows the spatial order since the other 
values are held constant in the case that deconvolution is requested.  Notice that there is typically no minimum.}
\label{fig-MSE_FITTED}
\end{figure}
